---
title: "Assignment 1 Task 1"
author: "AJ Zekanoski"
date: "1/20/2021"
output: html_document
---

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(ggfortify)
library(readxl)
library(gghighlight)
library(lubridate)
library(plotly)
library(patchwork)
library(palmerpenguins)
library(here)
```

#### Read in the Sierra Amphibians xlsx data and wrangle a bit.
```{r, warning=FALSE, message=FALSE}
sierra_amphibians <- read_excel(here("data", "sierra_amphibians.xlsx")) %>% 
  filter(amphibian_life_stage %in% c("Tadpole", "Adult", "SubAdult")) %>%
  filter(amphibian_species == "RAMU")
```


#### Wrangle some more with `lubridate` to get the year in its own column and then count observations.
```{r}
sierra_amphibians_2 <- sierra_amphibians %>% 
  mutate(survey_date = ymd(survey_date)) %>% 
  mutate(year = year(survey_date)) %>% 
  count(year, amphibian_life_stage, wt = amphibian_number) %>% 
  rename(count = n)
```


#### Plot counts of mountain yellow-legged frog plotted with ggplot.
```{r}
frog_plot_1 <- ggplot(data = sierra_amphibians_2, aes(x = year, y = count)) +
  facet_wrap(~amphibian_life_stage, scales = "free") +
  geom_col(fill = "gold") +
  labs(x = "", y = "") +
  theme_minimal()


```


#### Filter again to only have mountain yellow frogs in the adult and subadult life stages.
```{r}
sierra_amphibians_3 <- sierra_amphibians %>% 
  filter(amphibian_life_stage %in% c("Adult", "SubAdult"))
```

#### Rename the Lake Id column and get counts of frogs in top five lakes. 
```{r}
sierra_amphibians_4 <- sierra_amphibians_3 %>% 
  mutate(lake_id = paste0("Lake ", lake_id)) %>% 
  count(lake_id, wt = amphibian_number) %>% 
  rename(count = n) %>% 
  slice_max(count, n = 5)
```

#### Graph the counts of mountain yellow frogs in the top five lakes.

```{r}
frog_plot_2 <- ggplot(data = sierra_amphibians_4,
                      aes(x = fct_reorder(lake_id, -count), y = count)) +
  geom_col(width = 0.7, fill = "lightblue", show.legend = FALSE) +
  theme_minimal()


```

#### Create a combined graph with `patchwork` and add a sweet caption.
```{r, fig.cap = "**Figure 1**. Mountain yellow-legged frog abundance recorded by the Sierra Lakes Inventory Project from 1995-2002. Total abundance by life stage in all water bodies (above) and abundance of combined adults and subadults in the five most populated lakes (below) are displayed."}
 frog_plot_combined <-frog_plot_1 / frog_plot_2 + labs(x = "", y = "")

frog_plot_combined

```



